What is MaxEnt?

### 2014-11-24 ms.tex
minor words

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
knowledge about a vector of quantities $\mathbf{x}$. Consider some
function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $f$, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:expectations}.

@@

>>>>

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
knowledge about a vector of quantities $\mathbf{x}$. Consider some
function of the unknowns, such as $F=f(\mathbf{x}) = \sum_{i=1}^N x_i$.
If the value of $F$ is known, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $F$, then our distribution for $\mathbf{x}$ can
be updated as in Section~\ref{sec:expectations}.

@@

For any distribution $p(\mathbf{x})$, the marginal distribution for $F$ is:

\begin{eqnarray}
p(F) &=& \int \delta\left(F - f(\mathbf{x})\right)p(\mathbf{x}) \, d^n \mathbf{x}
\end{eqnarray}
